---
title: "faf_game_model"
format: html
editor: visual
---

## Creating a Model of the Forests and Foragers Tabletop Game

This document collects code intending to emulate the Forests and Foragers dice/card games as deployed at Bell Museum SciPride on 2024/06/29 in code for balancing purposes.

## Setup

```{r}
library(tidyverse)
```

## First Steps

It is probably sensible to build a set of lists (encounter cards, small mammals) and functions (card selector, choice selector, dice roller). Dice roller is a easy place to start.

### Dice Roller ( + mammals)

```{r}
## create dice roller function

## let's use sample as the base
sample(x = 1:6, size = 1)

## set variable nd as number of dice
nd <- 1
## set variable ds as dice sides (probably constant)
ds <- 6

## sample takes variables
sample(x = 1:ds, size = nd)
```

Adding any more to sample makes little sense without the mammal player stats. Let's make a mammal list:

```{r}
## creating mammal list as data frame (tibble)
mammals <- tibble(name = c("mouse", "shrew", "chipmunk"),
                  forage = c(2,2,1),
                  climb = c(2,1,2),
                  dig = c(1,2,2),
                  tick = rep(1,3),
                  bonus_type = c("climb", "forage", "pred"),
                  bonus_amt = c(1,2,1))

## test filter/select
test <- filter(mammals, name == "mouse") %>%
  select(c("forage","climb","dig", "tick")) %>%
  as.numeric()

## test roll all dice, take max of multiple
map_int(.x = test, .f = function(x){max(sample(1:6,x))})

## now dice rolling function that uses sample
dice_roll <- function(player, player_stats, dice_types = c("forage","climb","dig", "tick")){
  player_dice <- filter(player_stats, name == player) %>%
    select(all_of(dice_types)) %>%
    as.numeric()
  rolls <- map_int(.x = test, .f = function(x){max(sample(1:6,x))})
  names(rolls) <- dice_types
  return(rolls)
}

## test function
dice_roll(player = "mouse", player_stats = mammals)

## nice
```

Now to make the dice roller apply to a card...

### Card Selector + Cards

Start with a subset of cards that vary in dice types required. How to structure?
